Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-08 manuscript.tex
Reflow introduction [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/9d5c623b3eefb444db71bb9adfe13d2531bc9516.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/9d5c623b3eefb444db71bb9adfe13d2531bc9516/checks
https://github.com/habi/acinar-analysis-manuscript/runs/408125404

This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...bd33f8a44e5a603397d1f7fc7885ae6b754530aa}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/bd33f8a44e5a603397d1f7fc7885ae6b754530aa/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/bd33f8a44e5a603397d1f7fc7885ae6b754530aa}{habi/acinar-analysis-manuscript@bd33f8a}
on December 8, 2020.

@@

Here, the timing of lung development is given for rats while the same stages and developmental mechanisms are observed in every placentalian species studied so far, including humans.
However, the timing of lung development and especially the time point of birth relative to lung development is adapted in each species~(\protect\hyperlink{ref-XQLPrPTJ}{32}, \protect\hyperlink{ref-ODQCVC23}{33}, \protect\hyperlink{ref-d1YV8oOK}{35}).

@@

Pulmonary acini represent the gas-exchanging units of the bronchial tree and are defined as the airways distal of the terminal bronchioles~(\protect\hyperlink{ref-BbEFwEVD}{13}).
In humans, the acini contain approximately four generations of respiratory bronchioles before reaching the alveolar ducts.
The alveolar ducts start at the so-called bronchioalveolar duct junction (BADJ) where the lining of the inner airway surface abruptly changes from the cuboidal epithelium of the bronchioles into type 1 and type 2 alveolar epithelium which covers the alveoli.
The small tree of airways distal of the BADJ is called a ventilatory unit~(\protect\hyperlink{ref-WDrIHn9p}{39}).
Since murine lungs do not possess respiratory bronchioles, the murine acini consist of one single ventilatory unit~(\protect\hyperlink{ref-WDrIHn9p}{39}).
In \emph{this} study we used rat lungs; hence we exclusively speak of acini.
To translate our results to humans, monkeys, or dogs, one would have to compare a rat acinus to a single ventilatory unit in these species.

@@

However, besides the global numbers little is known about the range of the volume of individual acini throughout lung development.
The acinar architecture is important for ventilation, airflow~(\protect\hyperlink{ref-CVl41LwO}{8}, \protect\hyperlink{ref-eb0gk6VO}{14}, \protect\hyperlink{ref-1DP2FRUSZ}{16}) and particle deposition~(\protect\hyperlink{ref-18DcNLAv6}{22}, \protect\hyperlink{ref-yHHhvOtP}{36}, \protect\hyperlink{ref-wnl86DEM}{46}).
However, due to the lack of measured data, simulations are based on relatively simple acinar models.
The question of how well these models represent lung physiology remains open until the necessary data and physiologically correct models are available.
To contribute to the validation of the computational fluid dynamics simulations, we extracted individual acini and determined their volume and their number of alveoli throughout rat lung development.

@@

We developed the hereby presented method to analyze large amounts of acini over the course of postnatal lung development in a time-efficient manner since no data on large amounts of acini is available up to now.
Our aim was to understand the size distribution of the acini during lung development including the contribution of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents a completely unexpected result.
The obtained data are essential for further investigations, like the influence of the size of the acini on ventilation or gas-washout, respectively.
E.g., we are currently using our computational fluid dynamics model to simulate exactly this influence (own unpublished results and~(\protect\hyperlink{ref-eb0gk6VO}{14})).

>>>>

This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...9d5c623b3eefb444db71bb9adfe13d2531bc9516}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/9d5c623b3eefb444db71bb9adfe13d2531bc9516/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/9d5c623b3eefb444db71bb9adfe13d2531bc9516}{habi/acinar-analysis-manuscript@9d5c623}
on December 8, 2020.

@@

In this manuscript, the timing of lung development is given for rats while the same stages and developmental mechanisms are observed in every placentalian species studied so far, including humans.
However, the timing of lung development and especially the time point of birth relative to lung development is adapted in each species~(\protect\hyperlink{ref-XQLPrPTJ}{32}, \protect\hyperlink{ref-ODQCVC23}{33}, \protect\hyperlink{ref-d1YV8oOK}{35}).

@@

Pulmonary acini represent the gas-exchanging units of the bronchial tree and are defined as the airways distal of the terminal bronchioles~(\protect\hyperlink{ref-BbEFwEVD}{13}).
In humans, the acini contain approximately four generations of respiratory bronchioles before reaching the alveolar ducts.
The alveolar ducts start at the so-called bronchioalveolar duct junction (BADJ) where the lining of the inner airway surface abruptly changes from the cuboidal epithelium of the bronchioles into type 1 and type 2 alveolar epithelium which covers the alveoli.
The small tree of airways distal of the BADJ is called a ventilatory unit~(\protect\hyperlink{ref-WDrIHn9p}{39}).
Since murine lungs do not possess respiratory bronchioles, the murine acini consist of one single ventilatory unit~(\protect\hyperlink{ref-WDrIHn9p}{39}).
In this study we used rat lungs; hence we exclusively speak of acini.
To translate our results from rats to humans, monkeys, or dogs one would have to compare one rat acinus to one single ventilatory unit in these species.

@@

The acinar architecture is important for ventilation, airflow~(\protect\hyperlink{ref-CVl41LwO}{8}, \protect\hyperlink{ref-eb0gk6VO}{14}, \protect\hyperlink{ref-1DP2FRUSZ}{16}) and particle deposition~(\protect\hyperlink{ref-18DcNLAv6}{22}, \protect\hyperlink{ref-yHHhvOtP}{36}, \protect\hyperlink{ref-wnl86DEM}{46}).

@@

\hypertarget{aims-of-this-study}{%
\subsubsection{Aims of this study}\label{aims-of-this-study}}

\hypertarget{acinar-structure}{%
\paragraph{Acinar structure}\label{acinar-structure}}

Due to the lack of precise and complete three-dimensional data, simulations of airflow in the lung are based on relatively simple acinar models.
The question of how well these models represent lung physiology remains open until the necessary data and physiologically correct models are available.
To contribute to the validation of the computational fluid dynamics simulations, we extracted individual acini and determined their volume and their number of alveoli throughout rat lung development.

\hypertarget{individual-acinar-volumes}{%
\paragraph{Individual acinar volumes}\label{individual-acinar-volumes}}

While the global volume of the acini is well known and studied, only little is known about the range of the volume of individual acini throughout lung development.
We developed the hereby presented method to analyze large amounts of acini over the course of postnatal lung development in a time-efficient manner since no data on large amounts of acini is available up to now.
Our aim was to understand the size distribution of the acini during lung development including the contribution of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents a completely unexpected result.
The obtained data are essential for further investigations, like the influence of the size of the acini on ventilation or gas-washout, respectively.
E.g., we are currently using our computational fluid dynamics model to simulate exactly this influence (own unpublished results and~(\protect\hyperlink{ref-eb0gk6VO}{14})).
